Probing Galactic structure with moving groups and radial velocity surveys

### 2010-03-01 tex/ms.tex
groups-simulations: outline of methodology section
groups-simulations: abstract tweaks

\begin{abstract}
Various dynamical scenarios related to the Milky Way's bar or spiral
structure have been proposed to explain the existence of moving
groups---clumps of co-moving stars---in the Solar neighborhood. These
models are hard to distinguish with observations of the local Galactic
neighborhood. We show that future programs that survey the Milky Way
disk's kinematics on a global scale can distinguish between these
models. By integrating orbits of stars in various steady-state and
transient bar and spiral structure potentials that produce the pattern
of moving groups observed in the Solar neighborhood, we predict the
velocity distribution as a function of location in the Galactic
disk. We identify the locations that distinguish most clearly between
the various scenarios. Future infrared radial velocity surveys can
probe the velocity distribution at these locations; We predict the
distribution of radial velocities that can be directly compared to
observations to establish the origin of the moving groups and to
constrain the structural and dynamical parameters of the
non-axisymetric Milky Way potential.
\end{abstract}

@@

@@

>>>>

\begin{abstract}
Various dynamical scenarios related to the Milky Way's bar or spiral
structure have been proposed to explain the existence of moving
groups---clumps of co-moving stars---in the Solar neighborhood. Since
the observed pattern of moving groups is very sensitive to the
properties of the non-axisymmetric feature that creates them, these
moving groups can be a powerful tool in constraining the dynamical
structure of the inner Milky Way. However, at present the various
models are hard to distinguish with observations of the local Galactic
neighborhood. We show that future programs that survey the Milky Way
disk's kinematics on a more global scale can distinguish between these
models. By integrating orbits of stars in various steady-state and
transient bar and spiral structure potentials that produce the pattern
of moving groups observed in the Solar neighborhood, we predict the
velocity distribution as a function of location in the Galactic
disk. We identify the locations that distinguish most clearly between
the various scenarios. Future infrared radial velocity surveys can
probe the velocity distribution at these locations. We predict the
distribution of radial velocities that can be directly compared to
observations to establish the origin of the moving groups and to
constrain the structural and dynamical parameters of the
non-axisymmetric Milky Way potential.
\end{abstract}

@@

\section{Methodology}

We follow Dehnen's approach \citep{dehnen00a}.

\subsection{Bar potential}

\subsection{Steady-state spiral structure potential}

\subsection{Transient spiral structure potential}

@@

\bibitem[Dehnen(2000)]{dehnen00a}
  Dehnen,~W., 2000, \aj, 119, 800
